---
title: "Hazard Model"
---



```{r}
library(lme4)
```

```{r}
hotel = read.csv("HHonors_booking.csv", header=T)
interval = c( )
for(i in 1:400) {
   hotel.i = hotel[hotel$customerID==i,]
   interval.i = rep(0, 50)
   sinceBooking = 0
   for(t in 1:50) {
       sinceBooking = sinceBooking + 1
       interval.i[t] = sinceBooking
       if (hotel.i$Booking[t] == 1) sinceBooking = 0
   }
   interval = c(interval, interval.i)
}
hotel$Interval = interval  

```
We estimate the following logistic regression model using the R function glm( ) 

log(λi(t)/(1- λi(t)) = B0 + B1×Intervalit + B2×Priceit +B3×Promotionit 
                                  + B4×Incomei +B5×Genderi 
```{r}
hotel.logit = glm(Booking~Interval+Price+Promotion+Income+Gender, family = binomial (link=logit),data=hotel)
summary(hotel.logit)
```
B1 : When interval increases, the probability of booking will increase.
B2 : When price increases, the probability of booking will decrease.
B3: When there is a promotion, the probability of booking will not change.
B4: When income increases, the probability of booking will increase.
B5 : When gender changes, the probability of booking will not change.

Among these coefficients,B3 and B5 are not significant.

```{r}
hotel.logit2 = glm(Booking~ poly(Interval,2)+Price+Promotion+Income+Gender, family = binomial (link=logit),data=hotel)
summary(hotel.logit2)
```
B2,B4, B6 are not significant.
```{r}
AIC(hotel.logit)
AIC(hotel.logit2)
BIC(hotel.logit)
BIC(hotel.logit2)
```
The first model would seem superior.

We estimate the following cloglog regression model using the R function glm( ) 

log(-log(1- λi(t)) = B0 + B1×Intervalit + B2×Priceit +B3×Promotionit 
                                  + B4×Incomei +B5×Genderi
                                  
```{r}
hotel.clog = glm(Booking~Interval+Price+Promotion+Income+Gender, family = binomial (link=cloglog),data=hotel)
summary(hotel.clog)
```
B1: When interval increases, the probability of booking will increase.
B2: When price increases, the probability of booking will decrease.
B3: When there is a promotion, the probability of booking will not change.
B4: When income increases, the probability of booking will increase.
B5: When gender changes, the probability of booking will not change.
B3, B5  are not significant.

```{r}
AIC(hotel.clog)
BIC(hotel.clog)
```

Next, we will let the intercept be a random effect 0i in both the logistic and cloglog models

log(λi(t)/(1- λi(t)) = B0i + B1×Intervalit + B2×Priceit +B3×Promotionit 
                                  + B4×Incomei +B5×Genderi 
log(-log(1- λi(t)) = B0i + B1×Intervalit + B2×Priceit +B3×Promotionit 
                                  + B4×Incomei +B5×Genderi 
```{r}
hotel.logit3 = glmer(Booking~Interval+Price+Promotion+Income+Gender+(1|customerID),data=hotel, family = binomial(link="logit"))
summary(hotel.logit3)
```
```{r}
hotel.clog2 = glmer(Booking~Interval+Price+Promotion+Income+Gender+(1|customerID),data=hotel, family = binomial(link="cloglog"))
summary(hotel.clog2)
```
```{r}
AIC(hotel.logit3)
AIC(hotel.clog2)
BIC(hotel.logit3)
BIC(hotel.clog2)
```

The last model would seem to be the best one.

